An example Bayesian data analysis with PyMC:\\The TFR-HDI controversy

### 2011-07-04 tex/paper.tex
picture perfect linear model

@@

tfr = [d['tfr%d'%y] for y in years for d in all_data]
tfr = pl.ma.masked_array(tfr, pl.isnan(tfr))
\end{verbatim}
\caption{Listing of src/data.py}
\label{src/data.py}
\end{figure}
  \subsection*{Yet another sub-heading for this section}
    Text for this sub-section \ldots

>>>>

\usepackage{amsmath}
\def\TFR{\operatorname{TFR}}
\def\HDI{\operatorname{HDI}}

@@

tfr = [d['tfr%d'%y] for y in years for d in all_data]
tfr = pl.ma.masked_array(tfr, pl.isnan(tfr))
\end{verbatim}
\caption{Listing of src/data.py}
\label{src/data.py}
\end{figure}

  \subsection*{Model Building}
I started with the simplest relationship between HDI and TFR, which is
 a "linear model" that posits for a given increment in HDI there is a
 corresponding decrement in TFR, and formalizes this according to the
 equations
\begin{align*}
\TFR_i &= \beta_0 + \beta_1 \HDI_i + \epsilon_i\\
\epsilon_i &\sim N(0, \sigma^2)
\end{align*}
